Transfer Learning in Visual and Relational Reasoning

### 2020-02-13 Transfer_Learning/arxiv_version/submission_folder/v1/related_work.tex
Cleanup for arxiv version

\section{Related work}
Visual Question Answering (VQA) is a challenging multimodal task that combines vision and language.  Most image question answering datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations. Prior work generally relied on dense visual features produced by either CNNs~\cite{xiong2016dynamic,yang2016stacked} or object detection modules \cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings \cite{teney2017graph, santoro2017simple}.

>>>>

\section{Related work}
Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015} is a challenging multimodal task that combines vision and language.  Most Image Question Answering datasets and tasks focus on identifying object attributes, counting, and reasoning about their spatial-relations. Prior work generally relied on dense visual features produced by either CNNs~\cite{xiong2016dynamic,yang2016stacked} or object detection modules \cite{desta2018object}, and increasingly, recent models utilize the relationships among objects to augment those features with contextual information from each object’s surroundings \cite{teney2017graph, santoro2017simple}.
